\chapter*{Acknowledgments}
First and foremost, I would like to thank my supervisors, \emph{Farid Ould-Saada}, \emph{Eirik Gramstad} and \emph{James Catmore}. 
Without the guidance of all three of you, I would surely never have been able to finish this thesis. I have been incredibly
privileged that you have taken time out of your lives to meet with me every single week and discuss my work. 
I am particularly thankful that you have the patience to teach me the definition of jets every week, as well as
why neutrinos are not considered leptons.
\\\newline
To my family, who has never pushed education upon me, but have allowed me to follow what ever I desired, whether it was DJing or 
particle physics. A special thank you to my grandmother, \emph{Brenda Rose Hirst}, for never allowing me to leave the breakfast table 
without finishing my math puzzles.
\\\newline
To my friends, both those I made before and during my studies. In the opening speech of my bachelor's degree I was told by the speaker that 
the majority of students who do not finish their degree, do so as a result of lack of friends, not due to the difficulty of the degree.
Without my friends I would have no doubt joined that statistic. To the friends I made during my bachelor; thank you for all the espresso shots in \emph{RF-kjelleren}
and stupid, loud conversations in \emph{Vilhelm Bjerknes Hus}. To the friends I made during my masters; thank you for all the delicious toast we have shared, and 
incredible ping-pong wars we have fought. And to \emph{Sakarias}, for being with me through both my bachelors and my masters. I will never be able 
to watch \emph{Doctor Who} again without reminiscing of our time in the experimental physics course. Finally, thank you to \emph{Carl Martin} 
for being the co-creator of the codebase used to visualize the pathways of \acs{LWTA} layers displayed in this thesis. 
\\\newline
And finally, to my dear \emph{Martine}. Without you, I would not only have struggled to finish my thesis, but finishing it would be utterly 
meaningless.
