\subsection{Lepton Variables}\label{subsec:LepSel}
Information regarding the kinematics of the leptons were added into the data set: i.e. the transverse momentum, $P_t$, the pseudo 
rapidity $\eta$ and the azimuth angle $\phi$. All kinematic features were represented individually for each lepton. For example $P_t$
was added as three columns, $P_t(l_1)$, $P_t(l_2)$ and $P_t(l_3)$, where the ordering of the leptons were based on the momentum from highest ($l_1$) to lowest ($l_3$).
Similarly, I added information regarding the charge ($\pm$) and flavor (electron, muon) of each lepton. Based on the kinematic variables
the transverse mass $m_t$ of each lepton was calculated, $\Delta R$ and the energy, $E_t^{miss}$, and azimuth angle, $\phi^{miss}$,
of the missing transverse momentum.
\\
The variables described in the section above are often considered as low-level features. These are very useful in many (if not all)
searches and contribute little to no bias to your analysis. High-level features can be added to guide a hypothetical model 
in its search. The higher level features used in this analysis were inspired by several publications of \ac{ATLAS} I read in 
preparation of the analysis \cite{franchini_search_2019, atlas_search_2021}. 
\\
Firstly I added different mass variables, namely $m_{lll}$ and $m_{ll}(OSSF)$ (\ac{OSSF}). The first being the trilepton invariant mass 
and the latter being the dilepton invariant mass of the pair with \ac{OSSF}. In the case of more than one possible \ac{OSSF}-pair,
the pair with the highest invariant mass was chosen. Secondly I added variables composed of the sum of the transverse momenta.
These variables include the sum of all three leptons, $H_t(lll)$, of the pair with same sign/charge, $H_t(SS)$, and the sum of the momentum
for all three leptons added with the missing transverse energy $H_t(lll) + E_t^{miss}$. Finally, I added the significance of the
$E_t^{miss}$, $S(E_t^{miss})$.
\subsection{Jet Variables}\label{subsec:JetSel}
Now we can have a look at the jet-features. Given the final state of interest should be independent of jets, there are not many
features added with jet information. But, given the risk of miss identification and errors in reconstruction, some features were 
added. The first features added were the number of jets, both all signal\footnote{See section \ref{subsec:Cuts}.} jets and number of b-jets.
The latter information was divided in two columns based on the efficiency of a multivariate analysis used to separate jet-flavors.
The efficiencies used for b-tagging are $77\%$ and $85\%$. The last information added for the jets were the mass of the leading pair 
(based on $p_t$) di-jet mass, $m_{jj}$.
